Assignment 5

### 2015-02-24 rmtw/a5/latex8.tex
dsd

\SubSection{Statement of the Problem}

The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the the system requirements are and in which environment the system is developed. Selecting for example MDSD for the wrong system and setting may have a very negative impact on development speed, quality and maintainability. Since there seems to be a consensus in academia that MDSD is an improvement compared traditional software development \cite{staron2006adopting} \cite{volter2013model} and that most large software companies chose not to adopt MDSD, there is a need to methodically investigate the existing literature in which studies of the adoption of MDSD, and advantages and disadvantages of MDSD.

\SubSection{Existing Literature}

Good examples

Bad examples

What is the actual result, is it good or bad?

Why do they contradict, environment vs system?

@@

\SubSection{Notes4John}
\cite{volter2013model} says that MDSD will: increase development speed, increase quality, improve reusability, improved manageability through abstraction etc.

@@

Industry contradicts academia.

>>>>

\SubSection{Statement of the Problem}
The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the the system requirements are and in which environment the system is developed. Selecting for example MDSD for the wrong system and setting may have a very negative impact on development speed, quality and maintainability. Since there seems to be a consensus in academia that MDSD is an improvement compared traditional software development \cite{staron2006adopting} \cite{volter2013model} and that most large software companies chose not to adopt MDSD, there is a need to methodically investigate the existing literature in which studies of the adoption of MDSD, and advantages and disadvantages of MDSD.

\SubSection{Existing Literature}
According to literature, changes in companies are commonly implemented following either Software Process Improvement (SPI)\cite{pettersson2008practitioner}\cite{unterkalmsteiner2012evaluation} or change management (CM) strategies. SPI is an attempt to alter an existing company or organisations software process, the main intention of which is to increase product quality, time to market all the while reducing inefficiency and other obstacles for creating good software.

Similar to SPI is the concept of Evidence Based Software Engineering \cite{dyba2005evidence}. EBSE can be used as support for SPI, as suggested by the creators of the strategy. The main aim of which is to find a technology which is suitable for use and to then implement it in an organisation.

CM on the other hand could be seen as an umbrella for a plethora of theories and strategies. An example of a theory is the concept of innovation values fit by \cite{klein1996challenge} which aims to describe if and when a company should make changes, based upon how a potential change fits with the values currently held by the company.

In 2002 Hall, Rainer and Baddoo \cite{hall2002implementing} published a report wherein they illustrated results of a study which looked at 85 companies throughout the UK. The study focused mostly on how the companies perform SPI and how effective their efforts were. The authors discovered that, while most companies do attempt SPI, many are unsuccessful due to a combined lack of evaluation and funding.

@@

However, there is no existing research that aims to tackle the problem of applying the same change to an organisation that utilises two differing development paradigms. 
\SubSection{Notes4John}
\cite{volter2013model} says that MDSD will: increase development speed, increase quality, improve reusability, improved manageability through abstraction etc.

\SubSection{Notes4John2}
\cite{mattsson2009linking} talk about the link between MDSD and software architecture. They mention the importance of automatic enforcement of architectural rules and that MDSD is only benefecial if used correctly.

@@
